Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
SIstemato didascalie e immagini (tranne fig 3 che è in fase di elaborazione)

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Example of camera displacement. Left plots report the luma values, while right plots depict the detrended luma: we show both indicators computed over the full image (\textbf{a}) and on two reported regions (\textbf{b} and \textbf{c}). Red stars indicate a single displaced frame, which occurs at $t =157$. Displacement yields a peak in $l$ and two outliers in the sequence of detrended indicators $\partial l$, which can be clearly detected. }
\label{fig:indicatori} 
\end{figure}
%Tampering changes the sequence of indicators:
Figure~\ref{fig:indicatori}(a) shows how a camera displacement affects the luma. First of all, we observe that a displaced frame changes $l(t)$ (in this case introducing a peak) and that this change is also visible in the indicators $l_k(t)$ for the regions (Figure~\ref{fig:indicatori}(b) and Figure~\ref{fig:indicatori}(c)). Second, we observe that outlier-detection methods~\cite{Chandola2009} based on density estimates or on confidence intervals --that are very efficient to run-- cannot be straightforwardly applied here. In fact, these methods are meant for independent and identically distributed (i.i.d.) random variables, while here indicators follow an unpredictable trend because of changes in the scene or in the illumination. Therefore, we perform a detrending~\cite{Gustafsson2000} of the indicator sequence by a temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial d_k(t)$ and $\partial g(t)$.

@@

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $24410$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns. We have synthetically introduced $5\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring was simulated by convolution against a Gaussian kernel (as in Figure \ref{fig:sequences}(a)). \footnote{Sequences can be released upon request.}.
\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}

@@

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values \gi{quale?}. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene. Overall, the ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.

\emph{We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curve for displacement detection.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} (Luma-Region) is $99.94\%$, the AUC of Luma-Total is $99.89\%$ the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.96\%$) outperforms the Gradient-Regions (AUC $98.95\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
	\textbf{TODO} For the visualization sake, these ROC curves have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Example of camera displacement. 
Left plots report the luma values, while right plots depict the detrended luma: 
we show both indicators computed over the full image (\textbf{a}) and on two reported regions (\textbf{b} and \textbf{c}). Red dots indicate a single displaced frame. Values in the highlighted areas refer to the frames depicted on top of the fugure. 
Displacement yields a peak in $l$ and two outliers in the sequence of detrended indicators $\partial l$, which can be clearly detected. }
\label{fig:indicatori} 
\end{figure}
%Tampering changes the sequence of indicators:
Figure~\ref{fig:indicatori}(a) shows how a camera displacement affects the luma. First of all, we observe that a displaced frame changes $l(t)$ (in this case introducing a peak) and that this change is also visible in the indicators $l_k(t)$ for the regions (Figure~\ref{fig:indicatori}(b) and Figure~\ref{fig:indicatori}(c)). Second, we observe that outlier-detection methods~\cite{Chandola2009} based on density estimates or on confidence intervals --that are very efficient to run-- cannot be straightforwardly applied here. In fact, these methods are meant for independent and identically distributed (i.i.d.) random variables, while here indicators follow an unpredictable trend because of changes in the scene or in the illumination. Therefore, we perform a detrending~\cite{Gustafsson2000} of the indicator sequence by a temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial d_k(t)$ and $\partial g(t)$.

@@

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $24410$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns. We have synthetically introduced $10\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring was simulated by convolution against a Gaussian kernel (as in Figure \ref{fig:sequences}(a)). \footnote{Sequences can be released upon request.}.
%\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}

@@

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$, with step $0.1$. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene. Overall, the ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.

\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ Region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ Region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
	\textbf{(c)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
	For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
